Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-11-13 inst/doc/nonparametric-bayes.Rmd
added brief discussion of issues of priors and issues of value function curvature to the discussion

- All models are "good fits" to the originally observed data. 
- (Simple model choice immediately leads us astray)

@@

>>>>

- All models are "good fits" to the originally observed data. 
- (Simple model choice immediately leads us astray)
- Understanding the role of the prior

@@

### Risk-prone and Risk-adverse value functions

The degree to which the decision-making part of the algorithm (the SDP)
chooses to explore or avoid the resulting region of uncertainty can also
be influenced by the curvature of the value (profit) function $\Pi$. Both to simplify 
the intution and avoid biasing this result, we have chosen a profits that
are linear in the catch and thus neither risk-prone nor risk adverse.  Making
this function concave, representing the typical assumption of diminishing returns,
would make the SDP more risk-adverse (as larger-than-expected stock sizes offer
dimished returns relative to the cost of smaller-than-expected stock sizes), and 
strengthen the result shown here in which the BNP solution tends to avoid the 
region of uncertainty.  Sufficiently convex or risk-prone functions could lead
the SDP to attempt higher exploitation rates despite the uncertainty.  
Understanding the relative roles of such functions would be a promising direction
for future investigation.

### The role of the prior

Lastly, it should be noted that outside the data, the NBP reverts to the prior, 
and consequently the choice of the prior can also play a significant role in 
determining the optimal policy inferred by the SDP.  In the examples shown
here we have selected a prior that is both relatively uninformative (due to the 
broad priors placed on its parameters $\ell$ and $\sigma$ and simple (mean zero,
radial basis function kernel).  In practice, both the choice of mean and the 
choice of the covariance function may be chosen to confer particular biological
properties, as well as more biologically informed priors for $\ell$ and $\sigma$.  
In principle, this may allow a manager to improve the performance of the BNP-SDP
approach by adding only enough additional detail as is justified.  For instance,
it would be possible to use a linear or a Ricker-shaped mean in the prior without
making the much stronger assumption that the Ricker is the structurally correct model. 
However, this influence raises challenges as well.  For instance, in choosing a 
trivial mean-zero prior, we bias the dynamics to transitions to 0 in step $X_{t+1}$ 
from any stock size $X_t$ in the prior year, in the absence of any other data.  
Future research must make sure that both the prior and the value function are 
chosen appropriately for the problem at hand.
